Choosing Color Palettes for Data Visualization

### 2021-07-03 pkg/colorspace/paper/useR-2021/slides.Rnw
small touch-ups
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@603 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Robust Color Palettes for Data Visualization}

@@

\textbf{Base R:} Neglected better color palettes for a long time.

@@

\textbf{Earlier packages:} RColorBrewer, colorspace, ggplot2, viridis, rcartocolor, Polychrome, pals, paletteer, \dots

@@

\textbf{Thus:} Many good palettes easily available.

@@

\begin{minipage}{0.47\textwidth}
\textbf{HCL:} Polar coordinates in CIELUV. Captures perceptual dimensions of the human visual system very well.

@@

\setkeys{Gin}{width=\textwidth}
<<hcl-properties, fig = TRUE, width = 4, height = 2.2>>=
swatchplot(
  "Hue\n(Type of color)"       = sequential_hcl(5, h = c(0, 300), c = c(60, 60), l = 65),
  "Chroma\n(Colorfulness)"    = sequential_hcl(5, h = 0, c = c(100, 0), l = 65, rev = TRUE, power = 1),
  "Luminance\n(Brightness)" = sequential_hcl(5, h = 260, c = c(25, 25), l = c(25, 90), rev = TRUE, power = 1),
  nrow = 3, line = 5.2, off = 0
)
@
\end{minipage}
\pause
\hspace*{0.6cm}
\begin{minipage}{0.47\textwidth}
\textbf{RGB:} Motivated by how computers/TVs used to generate and still represent color.

@@

Luminance differences should be limited

@@

\vspace*{-0.5em}
\begin{footnotesize} 
\textbf{Risk map:} Probability of wind speeds $>$ 39\,mph (63\,km\,h$^{-1}$), 2019-08-30--2019-09-04.

\textbf{Source:} (\href{https://noaa.gov}{noaa.gov})
\end{footnotesize}

@@

\begin{minipage}[t]{0.65\textwidth}
\vspace*{-0.3cm}

@@

Web: \url{https://colorspace.R-Forge.R-project.org/}

@@

Twitter: \href{https://twitter.com/AchimZeileis}{\tt @AchimZeileis}

>>>>

\section{Choosing Color Palettes for Data Visualization}

@@

\textbf{Base R:} Neglected better color

palettes for a long time.

@@

\textbf{Earlier packages:} RColorBrewer,

colorspace, ggplot2, viridis,

rcartocolor, Polychrome, pals,

paletteer, \dots

@@

\textbf{Thus:} Many good palettes easily

available.

@@

\begin{minipage}{0.47\textwidth}
\textbf{HCL:} Polar coordinates in CIELUV.

Captures perceptual dimensions of

the human visual system very well.

@@

\setkeys{Gin}{width=\textwidth}
<<hcl-properties, fig = TRUE, width = 4, height = 2.2>>=
swatchplot(
  "Hue\n(Type of color)"       = sequential_hcl(5, h = c(0, 300), c = c(60, 60), l = 65),
  "Chroma\n(Colorfulness)"    = sequential_hcl(5, h = 0, c = c(100, 0), l = 65, rev = TRUE, power = 1),
  "Luminance\n(Brightness)" = sequential_hcl(5, h = 260, c = c(25, 25), l = c(25, 90), rev = TRUE, power = 1),
  nrow = 3, line = 5.2, off = 0
)
@
\end{minipage}
\pause
\hspace*{0.6cm}
\begin{minipage}{0.47\textwidth}
\textbf{RGB:} Motivated by how computers

and TVs used to generate and still

represent color.

@@

Luminance differences should be limited.

@@

\vspace*{-0.5em}
\begin{footnotesize} 
\textbf{Risk map:} Probability of wind speeds $>$ 39\,mph (63\,km\,h$^{-1}$), 2019-08-30--2019-09-04

\textbf{Source:} National Oceanic and Atmospheric Administration (\href{https://noaa.gov}{noaa.gov})
\end{footnotesize}

@@

\begin{minipage}[t]{0.64\textwidth}
\vspace*{-0.3cm}

@@

\textbf{Web:} \url{https://colorspace.R-Forge.R-project.org/}

@@

\textbf{Twitter:} \href{https://twitter.com/AchimZeileis}{\tt @AchimZeileis}
